Magnetic Phase Transitions in an Aperiodic Monotile

### 2023-06-09 paper/main.tex
Debugging quantum

\documentclass[amsmath,amssymb,aps,twocolumn]{revtex4-2}

@@

The phenomenon of critical temperature has been generalized to other theories. In particular, if the system's variables are arranged as a members of a field $s(\bm x)$, then the free energy automatically comes in a form that allows phase transitions using a method known as Landau field theory. Taking the Ising model as an example, we could approximate the $s_i$ spins defined on discrete points $x_i$ as a field $s(\bm x)$ defined for any position $\bm x$. The original Hamiltonian contained translational, rotational, and $s\rightarrow-s$ symmetry, and therefore the free energy should as well. Expanding it in powers of $s(\bm x)$ guarantees the form
\begin{equation}
F \propto -\int d^d x \, \parens{(\nabla s(\bm x))^2 + A s(\bm x)^2 + B s(\bm x)^4 + \dots}
\label{eqn:landau}
\end{equation}
where $d$ is the number of dimensions of the lattice and $A$ and $B$ are arbitrary constants. If $A>0$, then free energy is minimized at every point by setting $s(\bm x)$. However, if $A<0$, then minimizing the free energy necessitates setting $s(\bm x)$ to some nonzero value, thereby magnetizing the crystal and creating a phase transition. In principle, all the parameters of the model including $A$ may depend on temperature. All that is necessary to describe a phase transition is therefore to write a form of $A$ which allows it to cross from positive to negative at a critical temperature $T_c$.

The utility of this field theory approximation is in its generality. The Ising model and all models like it are Landau field theories and are therefore described by the sameEq.~\ref{eqn:landau}. Therefore, all Ising models have the same near-critical-point behavior regardless of the lattice on which they are defined. An Ising model's only unique properties are their values of $A$ and $B$; i.e., the value of the critical temperature.

@@

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.49\linewidth]{../figs/square.png}\hfill
  \includegraphics[width=0.49\linewidth]{../figs/square.png}
  \caption{Magnetization and susceptibility as a function of $T_c$ under the XY and Ising models. \textit{Left}: A square lattice with $N=128^2=16,384$ sites. \textit{Right}: A Penrose lattice with $N=21,316$ sites.}
  \label{fig:square}
\end{figure*}

>>>>

\documentclass[amsmath,amssymb,aps,twocolumn,nofootinbib]{revtex4-2}

@@

The phenomenon of critical temperature has been generalized to other theories. In particular, if the system's variables are arranged as a members of a field $s(\bm x)$, then the free energy may be approximated as an integral over functions of $s(\bm x)$. This approximation is called Landau Field Theory and it yields a form which is readily able to create phase transitions. Taking the Ising model as an example, we could approximate the $s_i$ spins defined on discrete points $x_i$ as the field $s(\bm x)$ defined for any position $\bm x$. The original Hamiltonian contained translational, rotational, and $s\rightarrow-s$ symmetry, and therefore the free energy should as well. Expanding it in powers of $s(\bm x)$ guarantees the form
\begin{equation}
F \propto -\int d^d x \, \parens{(\nabla s(\bm x))^2 + A s(\bm x)^2 + B s(\bm x)^4 + \dots}
\label{eqn:landau}
\end{equation}
where $d$ is the number of dimensions of the lattice and $A$ and $B$ are arbitrary constants. If $A>0$, then free energy is minimized at every point by setting $s(\bm x)$. However, if $A<0$, then minimizing the free energy necessitates setting $s(\bm x)$ to some nonzero value, thereby magnetizing the crystal and creating a phase transition. In principle, all the parameters of the model including $A$ may depend on temperature. All that is necessary to describe a phase transition is therefore to write a form of $A$ which allows it to cross from positive to negative at a critical temperature $T_c$.

The utility of this field theory approximation is in its generality. All Ising-like models like it are Landau field theories and are all described by Eq~\ref{eqn:landau}, meaning they have the same near-critical-point behavior. This statement is independent of the lattice or interaction strengths; it depends only on the field $\bm s$ and the dimensionality of the lattice. A particular lattice's only unique properties its its values of $A$ and $B$; i.e., the value of its critical temperature.

@@

We implemented the Wolff algorithm with a custom code base \footnote{\jtd{LINK}} and executed for a variety of spin models and crystals. Except when stated otherwise, we used a finite-size lattice with initial conditions of random spins. Magnetization $M$ and susceptibility $\chi$ measurements were collected every 16 cluster flips to prevent autocorrelation. 10,000 $M$ and $\chi$ measurements were made when $M$ was small, and when $M$ was large we made 1,000 measurements because the algorithm was found to be more stable for $T< T_c$.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.49\linewidth]{../figs/square.png}\hfill
  \includegraphics[width=0.49\linewidth]{../figs/penrose.png}
  \caption{Magnetization and susceptibility as a function of $T_c$ under the XY and Ising models. \textit{Left}: A square lattice with $N=128^2=16,384$ sites. \textit{Right}: A Penrose lattice with $N=21,316$ sites.}
  \label{fig:square}
\end{figure*}
